% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{Continuing Personal Development Report}

% Please do not change the subtitle
\subtitle{COMP240 - CPD Report}

% Please put your student number in the author field
\author{1603748}

\begin{document}

\maketitle

\section*{Introduction}
My career goals remain the same, I would like to be a game developer, I am still unsure what exactly I what to do within the industry however. After doing the business case report I would like to experiment with both self publishing and taking publisher deals. I would like to work in an indie team and would also like to work in a AAA company. Over the last term I think my programming knowledge has improved quite a lot, I am now much more confident and now know C sharp and Java fairly well. I'm glad that I have programmed in various different languages as it broadens my programming competency. Five key challenges I have faced this term were, team work, motivation, productiveness, assignment time management, and prioritising. To overcome not working very well as a team I will get to know my team as early as possible next year as I find it much easier to communicate with people I know. To improve my motivation I am going to create a self improvement/gratitude journal to track my work and make me feel better and hopefully more motivated to do work. This journal should also help me be more productive because I will set myself tasks to complete each day so I won't spend to much time not knowing what to work on. To improve assignment time management I will look at the module guides and make sure I work on each assignment for the right amount of time by tracking my hours on a spreadsheet. I will overcome my prioritising problem by using the spreadsheet for time management to set my goals for each day so I do the right amount of work for each assignment. 

\section{Team Work}
Team work is an extremely essential skill to have when developing games. You are always going to be working in a team in the industry so being able to work well in a team and communicate effectively is very important. This term I have struggled with this mainly because I didn't get to know my team very well. I find it much easier to communicate and collaborate with people that I know well personally. To improve this I will talk to my team next year more often at the start of the year to get to know everyone well which I believe will really improve how much I communicate with the team and therefore produce more work. 

\section{Motivation}
Motivation is key to getting a lot of good work done, without motivation it is almost impossible to be productive and do a sufficient amount of work each day. This term I have often lacked motivation to do work, sometimes it's just for certain assignments and sometimes I have no motivation to do any work. To hopefully improve my motivation I am going to make a self improvement/gratitude journal. In the journal I will set myself 3 goals to complete each day and if I complete all 3 it counts as a day I have "won", this should make me feel proud of the work I do and motivate me to "win" as many days as I can.   

\section{Productiveness}
Productiveness is also very important in the industry and doing any work in general. I would like to become a lot more productive as sometimes I feel that I am the opposite of productive. This term i have spent a lot of time procrastinating, when I try to do work I often get distracted and end up doing something else for a while. Using my self improvement/gratitude journal I feel that I can improve my productiveness by setting my self 3 goals each day. This will mean I will know what to work on and I will want to complete all of my goals for the day to feel good about myself. 

\section{Assignment Time Management}
I have never been great at time management, I usually just work on whatever I feel like working on or whatever is due next. This is obviously not a good way to work. If I improved my time management for all my assignments, the quality of my work would be good for all of my assignments rather than just a few of them. I will use the module guides to plan out how many hours I should spend on each assignment and create a spreadsheet to track my hours. I will use this spreadsheet to decide what my 3 goals are for the day.   

\section{Prioritising}
I tend to prioritise work that I enjoy doing more rather than managing my time between all of my work. I am aware of this and tell myself to not work on the project I enjoy because I have been working on it too much, but then I end up procrastinating because I don't want to work on the other assignments. Hopefully my journal will improve my motivation to work on other assignments. I think that I might enjoy other assignments more if I put some more time into them, it is just the first step that is hard.     

\section*{Conclusion}
In conclusion I have identified five key skills and how I plan to improve overcome them using a journal to track my progress, motivate me, and improve my productiveness. In addition I will track my hours for all the work I do in a spreadsheet and use that to decide what my goals will be for each day. My long term goal is complete all of my daily goals for a whole month and see how I have improved.  


\bibliographystyle{ieeetran}
\bibliography{references}

\end{document}
