% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{Continuing Personal Development Report}

% Please do not change the subtitle
\subtitle{COMP230 - CPD Report}

% Please put your student number in the author field
\author{1603748}

\begin{document}

\maketitle

\section*{Introduction}
My career goals haven't changed since last year, I still aspire to being a successful game developer in the future whether that is through starting a small indie development team, working in a large company and making AAA games or even freelancing. Now that I am half way through this degree I feel that I have learnt a huge amount about game development and believe that I have developed some good programming/scripting skills through making games and working on various projects involving programming. Five key challenges I have faced this term were communication, asking for help, problem solving, programming proficiency, and dedication. I will highlight these five skills in my report by acknowledging the challenges I faced then suggesting how I will overcome the obstacle in relation to a SMART action.

\section{Communication}
Communication is a very important skill you must have to develop games as a team, which is how every game is developed, as a team. The whole team should know what the rest of the team is currently working on, especially the members of the same specialism as you to avoid conflicted versions. This is something I struggled with last year, I have improved since then however I still don't communicate as much as I should with my team. It has caused problems such as working on the same or a very similar task to another member of the team, or me not sharing an idea with the team. To overcome this I plan to communicate my ideas with everyone and not be too shy to say anything, and whenever I am working on something I will let my team know what I am doing.

\section{Asking for help}
I often find myself struggling to complete a task but always trying to solve it on my own, rather than asking someone for help. Asking for help from others is very important to speed up the learning process as they point you in the right direction so you avoid wasting time. This term there has been many times where I should have asked for help because I didn't understand how to solve the problem I was dealing with, however I instead spent hours trying to figure out on my own. This is a big problem that I would like to change for future to improve my learning, particularly in programming. I will ensure that if I spent to much time on a task or do not understand it I will ask someone for help, whether that is another student or a lecturer. 

\section{Problem Solving}
Problem solving is an extremely important skill to have for a programmer. When developing games you problem solve all the time, you're always figuring out the best way to do something, or how to do something. This term I have had countless problems, some of which I could solve quite easily, however a fair amount I found very challenging and spent far too much time trying to solve. I would like to develop my problem solving skills in order to prevent spending too long on tasks and to become a better computing professional. To practice problem solving I will complete challenges on hackerrank.com which has lots of programming problems to solve to improve your programming and problem solving skill. I will complete at least 5 challenges a week.

\section{Programming Proficiency}
This term I have been working in C++ a lot more than last year and I have also learnt C\#. I am still fairly new to these languages and still have much to learn about them. I feel that my programming skill is not up to standard sometimes when I encounter problems and don't know how to solve them, this is a big issue as I should be able to solve these kind of problems if I want to be able to develop games for a living. I have learned what I have so far about these languages mainly through experience using them in assignments and projects, however I should also put in extra hours to practice programming. To do this I will complete online programming challenges on websites such as hackerrank.com, I set myself a goal of how many to complete each week to measure my progress.

\section{Dedication}
A common problem I have is postponing my work because I just don't feel like doing it and lack the motivation. This shouldn't be an excuse to not do work, I should do my work no matter how motivated I am. My dedication to doing work has been lacking this term and I need to improve it if I want to get my work done and become a more productive computing professional. I will improve my dedication by rewarding myself after doing work, especially if it is work I did not feel motivated to do. Hopefully after getting into the habit of doing work when it should be done I will not have to reward myself as my dedication would have improved.

\section*{Conclusion}
In this report I have identified 5 key skills that I have found challenging this term and have suggested how I will improve these skills and overcome the challenges I have encountered this term. By doing the tasks I have set myself in this report I will improve these skills and hopefully become a more professional game developer for next year and for the rest of my future career.

\bibliographystyle{ieeetran}
\bibliography{references}

\end{document}
